XXX in a Tracing JIT Compiler for Efficient Dynamic Languages

### 2011-03-27 talk/icooolps2011/paper.tex
give a conceptual level view on the hints

In this paper we present two of these hints that are extensively used in the
PyPy project to improve the performance of its Python interpreter. These
hints are used to control how the optimizer of the tracing JIT can improve the
traces of the object model. More specifically, these hints influence the
constant folding optimization. The first hint make it possible to turn arbitrary
variables in the trace into constants. The second hint allows the definition of
additional foldable operations.

@@

XXX replace "turn variable into constant" into "main tool to feedback language
and semantics specific runtime information into the compilation"

The contributions of this paper are:
\begin{itemize}
 \item A hint to turn arbitrary variables into constants in the trace.
 \item A way to define new pure operations which the constant folding
 optimization then recognizes.
 \item A worked-out example of a simple object model of a dynamic language and
 how it can be improved using these hints.
\end{itemize}

>>>>

In this paper we present two of these hints that are extensively used in the
PyPy project to improve the performance of its Python interpreter.

Conceptually the significant speed-ups that can be achieved with
dynamic compilation depends on feeding into compilation and exploiting
values observed at runtime that are in practice mostly constant (XXX or should we say slow varying), and
in structuring implementation code and data structures such that more
of such values are at hand. The hints that we present allow exactly to implement such feedback and exploitation in a meta-tracing context.

Concretely these hints are used to control how the optimizer of the
tracing JIT can improve the traces of the object model. More
specifically, these hints influence the constant folding
optimization. The first hint make it possible to turn arbitrary
variables in the trace into constant. The
second hint allows the definition of additional foldable operations.

@@

The contributions of this paper are:
\begin{itemize}
 \item A hint to turn arbitrary variables into constants in the trace, that means the feedback of runtime information into compilation.
 \item A way to define new pure operations which the constant folding
 optimization then recognizes.
 \item A worked-out example of a simple object model of a dynamic language and
 how it can be improved using these hints.
\end{itemize}
